Solar wind discontinuities spatial evolution in the outer heliosphere

### 2024-03-15 index.qmd
update

>>>>

### 02/27/2024

::: {.column-screen}
::: {#fig-evolution-juno layout-nrow="1"}
![Evolution of plamsa property using fitting method](figures/l_j_r_fit.png)

![Evolution of plamsa property using derivative method](figures/l_j_r_der.png)

From top to bottom is Juno observation in 1,2,3,4,5 AU
:::
:::

### 02/26/2024

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/06_corr_julia.ipynb#fig-l-comp >}}
:::

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/06_corr_julia.ipynb#fig-l-j-r-der >}}
:::

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/06_corr_julia.ipynb#fig-l-r-fit >}}

{{< embed notebooks/06_corr_julia.ipynb#fig-l-r-der >}}
:::

### 02/25/2024

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/05_sea.ipynb#fig-fit >}}

{{< embed notebooks/05_sea.ipynb#fig-fit-params >}}
:::

### 02/22/2024

::: {.column-screen layout-nrow="1"}
![First Year](figures/sea/sea_juno_first_year_high.png)

![Last Year](figures/sea/sea_juno_last_year_high.png)
:::

### 02/20/2024
